Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654

### 2016-08-15 WRITEUP/ms.tex
add ack RP,DR

%==============================================================================
%                                Back matters
%==============================================================================
% ACKNOWLEDGEMENTS
%-----------------
\acknowledgments
This work is based on observations carried out under project number S14BX
with the IRAM NOEMA Interferometer. IRAM is supported by INSU/CNRS (France), MPG (Germany) and IGN (Spain).
Support for CARMA construction was derived from the Gordon and Betty Moore
Foundation, the Kenneth T. and Eileen L. Norris Foundation, the James S.
McDonnell Foundation, the Associates of the California Institute of
Technology, the University of Chicago, the states of Illinois, California, and
Maryland, and the National Science Foundation. Ongoing CARMA development and
operations are supported by the National Science Foundation under a
cooperative agreement and by the CARMA consortium universities.
The National Radio Astronomy Observatory is a facility of the National Science
Foundation operated under cooperative agreement by Associated
Universities, Inc.
This research made use of data obtained with {\it Herschel}, an ESA space
observatory with science instruments provided by European-led Principal
Investigator consortia and with important participation from NASA.
This research has made use of NASA's Astrophysics Data System Bibliographic
Services.
This work is based in part on observations made with the \spitzer,
which is operated by the Jet Propulsion Laboratory, California Institute of
Technology under a contract with NASA.
This publication made use of data products from the Wide-field Infrared
Survey Explorer, which is a joint project of the University of California, Los
Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
funded by the National Aeronautics and Space Administration.
This publication made use of data products from the Two Micron All Sky
Survey, which is a joint project of the University of Massachusetts and the
Infrared Processing and Analysis Center/California Institute of Technology,
funded by the National Aeronautics and Space Administration and the National
Science Foundation.
This research made use of the NASA/IPAC Extragalactic Database (NED) which
is operated by the Jet Propulsion Laboratory, California Institute of
Technology, under contract with the National Aeronautics and Space
Administration.
This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
This research made use of APLpy, an open-source plotting package for Python hosted at \url{http://aplpy.github.com}.

>>>>

%==============================================================================
%                                Back matters
%==============================================================================
% ACKNOWLEDGEMENTS
%-----------------
\acknowledgments
DR and RP acknowledge support from the National Science Foundation
under grant number AST-1614213 to Cornell University. RP acknowledges
support through award SOSPA3-008 from the NRAO. DR acknowledges the
hospitality at the Aspen Center for Physics and the Kavli Institute
for Theoretical Physics during part of the writing of this manuscript.
This work is based on observations carried out under project number S14BX
with the IRAM NOEMA Interferometer. IRAM is supported by INSU/CNRS (France), MPG (Germany) and IGN (Spain).
Support for CARMA construction was derived from the Gordon and Betty Moore
Foundation, the Kenneth T. and Eileen L. Norris Foundation, the James S.
McDonnell Foundation, the Associates of the California Institute of
Technology, the University of Chicago, the states of Illinois, California, and
Maryland, and the National Science Foundation. Ongoing CARMA development and
operations are supported by the National Science Foundation under a
cooperative agreement and by the CARMA consortium universities.
The National Radio Astronomy Observatory is a facility of the National Science
Foundation operated under cooperative agreement by Associated
Universities, Inc.
This research made use of data obtained with {\it Herschel}, an ESA space
observatory with science instruments provided by European-led Principal
Investigator consortia and with important participation from NASA.
This research has made use of NASA's Astrophysics Data System Bibliographic
Services.
This work is based in part on observations made with the \spitzer,
which is operated by the Jet Propulsion Laboratory, California Institute of
Technology under a contract with NASA.
This publication made use of data products from the Wide-field Infrared
Survey Explorer, which is a joint project of the University of California, Los
Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
funded by the National Aeronautics and Space Administration.
This publication made use of data products from the Two Micron All Sky
Survey, which is a joint project of the University of Massachusetts and the
Infrared Processing and Analysis Center/California Institute of Technology,
funded by the National Aeronautics and Space Administration and the National
Science Foundation.
This research made use of the NASA/IPAC Extragalactic Database (NED) which
is operated by the Jet Propulsion Laboratory, California Institute of
Technology, under contract with the National Aeronautics and Space
Administration.
This research made use of Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
This research made use of APLpy, an open-source plotting package for Python hosted at \url{http://aplpy.github.com}.
